---
title: "Clémence parts"
author: "HUANG Clémence"
format: html
editor: visual
---

# 1. Introduction
[Link to our github repository](https://github.com/clemence-code/Data_management_Project)

## 1.1 Description of the project - Research question

For our project, we want to build our own index of climate vulnerability by combining three main dimensions: Exposure, Sensitivity, and Adaptive Capacity. For Exposure, we’ll look at how much each country is exposed to climate hazards, using data from the OECD. For Sensitivity, we’ll include social and economic factors like poverty rates, the Human Development Index, governance quality, and income inequality. For Adaptive Capacity, we’ll use indicators that show how well a country can respond and adapt to climate change, such as renewable energy production, environmental policies and research spending. 

## 1.2 Description of the sources

- OECD
  - [Historical exposure to extreme temperatures (0ECD, 1979-2024)](https://data-explorer.oecd.org/vis?bp=true&df[ds]=dsDisseminateFinalDMZ&df[id]=DSD_ECH%40EXT_TEMP_H&df[ag]=OECD.ENV.EPI&df[vs]=2.0&dq=AFG%2BBFA%2BBDI%2BCAF%2BTCD%2BSWZ%2BETH%2BGUF%2BATF%2BGLP%2BHMD%2BVAT%2BKAZ%2BXKV%2BKGZ%2BLAO%2BLSO%2BLIE%2BMWI%2BMLI%2BMTQ%2BMDA%2BMNG%2BNPL%2BNER%2BNFK%2BMKD%2BPRY%2BREU%2BRWA%2BSMR%2BSRB%2BSGS%2BSSD%2BTJK%2BTKM%2BUGA%2BUMI%2BUZB%2BZMB%2BZWE%2BIOT%2BBVT%2BBWA%2BBOL%2BBTN%2BBLR%2BAZE%2BARM%2BAND%2BCHE%2BSVK%2BLUX%2BHUN%2BCZE%2BAUT%2BALB%2BDZA%2BASM%2BAGO%2BAIA%2BATG%2BARG%2BABW%2BBHS%2BBHR%2BGGY%2BBGD%2BBRB%2BBLZ%2BBEN%2BBMU%2BBIH%2BBRA%2BVGB%2BBRN%2BBGR%2BCPV%2BKHM%2BCMR%2BCYM%2BCHN%2BCXR%2BCOM%2BCOG%2BCOK%2BCIV%2BHRV%2BCUB%2BCYP%2BPRK%2BCOD%2BDJI%2BDMA%2BDOM%2BECU%2BEGY%2BSLV%2BGNQ%2BERI%2BFRO%2BFJI%2BPYF%2BGAB%2BGMB%2BGEO%2BGHA%2BGRL%2BGRD%2BGUM%2BGTM%2BGIN%2BGNB%2BGUY%2BHTI%2BHND%2BHKG%2BIND%2BIDN%2BIRN%2BIRQ%2BIMN%2BJAM%2BJEY%2BJOR%2BKEN%2BKIR%2BKWT%2BLBN%2BLBR%2BLBY%2BMAC%2BMDG%2BMYS%2BMDV%2BMLT%2BMHL%2BMRT%2BMUS%2BMYT%2BFSM%2BMCO%2BMNE%2BMSR%2BMAR%2BMOZ%2BMMR%2BNAM%2BNRU%2BNCL%2BNIC%2BNGA%2BNIU%2BMNP%2BOMN%2BPAK%2BPLW%2BPSE%2BPAN%2BPNG%2BPER%2BPHL%2BPCN%2BPRI%2BQAT%2BROU%2BRUS%2BSHN%2BKNA%2BLCA%2BSPM%2BVCT%2BWSM%2BSTP%2BSAU%2BSEN%2BSYC%2BSLE%2BSGP%2BSLB%2BSOM%2BZAF%2BLKA%2BSDN%2BSUR%2BSJM%2BSYR%2BTWN%2BTZA%2BTHA%2BTLS%2BTGO%2BTKL%2BTON%2BTTO%2BTUN%2BTCA%2BTUV%2BUKR%2BARE%2BVIR%2BURY%2BVUT%2BVEN%2BVNM%2BWLF%2BESH%2BYEM%2BAU1%2BAU2%2BAU3%2BAU4%2BAU5%2BAU6%2BAU7%2BAU8%2BAUS%2BBEL%2BCAN%2BCHL%2BCOL%2BCRI%2BDNK%2BEST%2BFIN%2BFRA%2BDEU%2BGRC%2BISL%2BIRL%2BISR%2BITA%2BJPN%2BKOR%2BLVA%2BLTU%2BMEX%2BNLD%2BNZL%2BNOR%2BPOL%2BPRT%2BSVN%2BESP%2BSWE%2BTUR%2BGBR%2BUSA%2BG7%2BG20%2BEA19%2BEU27%2BOECD%2BOECDA%2BOECDSO%2BOECDE%2BAES%2BEMES%2BIPAC.A..........&fc=Topic&fs[0]=Topic%2C1%7CEnvironment%20and%20climate%20change%23ENV%23%7CAir%20and%20climate%23ENV_AC%23&pg=0&snb=13&to[TIME_PERIOD]=false&pd=%2C&vw=tb)
  - [Environmental Policy Stringency indicator (EPS)](https://data-explorer.oecd.org/vis?lc=en&tm=environmental%20policy&pg=0&snb=94&df%5bds%5d=dsDisseminateFinalDMZ&df%5bid%5d=DSD_EPS%40DF_EPS&df%5bag%5d=OECD.ECO.MAD&df%5bvs%5d=1.0&dq=.A..EPS&to%5bTIME_PERIOD%5d=false&pd=%2C&vw=tb)
- Human development report : [Index of Human Development (1990-2025)](https://hdr.undp.org/data-center/human-development-index#/indicies/HDI)
- World inequality database : [Income share of the top 10% and top 10% carbon emitters (1980-2023)](https://wid.world/data/)
- EMBER : [Electricity production from renewable sources (1985-2024)](https://ember-energy.org/data/yearly-electricity-data/)
- World bank :
  - [Per capita energy use (1990-2023)](https://data.worldbank.org/indicator/EG.USE.PCAP.KG.OE)
  - [R&D spending as a share of GDP (1996-2023)](https://data.worldbank.org/indicator/GB.XPD.RSDV.GD.ZS)

## 1.3 Description of the data file

## 1.3.0 Set up

```{r}
library(vroom)

```

importation librairies

### 1.3.1 Historical exposure to extreme temperatures
- description rapide des variables
- number rows, columns, NA
- années
- pays
### 1.3.2 Human Development index

### 1.3.3 Income share of the top 10%

### 1.3.4 Environmental Policy Stringency

### 1.3.5 Share of electricity from renewable resources

### 1.3.6 Per capita energy use

### 1.3.7 Research and development as a share of GDP

### 1.3.8 ND-Gain vulnerability index
```{r}

```


### 1.3.9 CO2 emissions per capita
```{r}

```


# 2. Data set up

cleaning joining merging

