---
title: "Valentine parts"
author: "Valentine Petzold"
format: html
---


# 1. Introduction
[Link to our github repository](https://github.com/clemence-code/Data_management_Project)

## 1.1 Description of the project - Research question

## 1.2 Description of the sources

OECD
World Bank 

+ links to the sources

## 1.3 Description of the data file

## 1.3.0 Set up
importation librairies

```{r}
library(vroom)
library(here)
library(ggplot2)
```
```{r}
here::i_am('Data_management_Project.Rproj')
```




#### Unzipping the files
```{r}
#zip_files <- list.files(
#  here("raw_data"),
#  pattern = "\\.zip$",
#  full.names = TRUE
#)

#for (f in zip_files) {
#  unzip(f, exdir = here("data_file"))
#}
```

- description rapide des variables
- number rows, columns, NA
- années
- pays

### 1.3.1 Historical exposure to extreme temperatures ##### MAL CHARGE

```{r}
library(readxl)
Temperature_exposure<-read_excel("raw_data/OECD.ENV.EPI,DSD_ECH@EXT_TEMP_H,2.0,filtered,2025-11-19 13-23-57.xlsx", skip=8)
```

### 1.3.2 Human Development index

```{r}
HDI <- read_excel("raw_data/HDR25_Statistical_Annex_HDI_Table.xlsx.", skip=4)
```


### 1.3.3 Income share of the top 10%

```{r}
Top_10 <- vroom(here("data_file/WID_Data_Metadata", "WID_Data_19112025-132927.csv"), delim=";",skip=1)#need to skip the first raw
```

### 1.3.4 Environmental Policy Stringency

```{r}
Environmental_Policy_Stringency_Index<- read_excel("raw_data/OECD.ECO.MAD,DSD_EPS@DF_EPS,1.0,filtered,2025-11-19 13-27-34.xlsx", skip=6)
```

### 1.3.5 Share of electricity from renewable resources

```{r}
Renewable_Electricity_Share<- vroom(here("raw_data", "yearly_full_release_long_format.csv"))
```

### 1.3.6 Per capita energy use

```{r}
PC_Energy_Use<- vroom(here("data_file", "Metadata_Country_API_EG.USE.ELEC.KH.PC_DS2_en_csv_v2_129274.csv"))
```

### 1.3.7 Research and development as a share of GDP

```{r}
RandD_share_of_GDP<- vroom(here("data_file", "API_GB.XPD.RSDV.GD.ZS_DS2_en_csv_v2_216043.csv"), skip=4)
```


### 1.3.8 ND-Gain vulnerability index

```{r}
capacity<- vroom(here("data_file/resources/vulnerability", "capacity.csv"))
```
```{r}
ecosystems<- vroom(here("data_file/resources/vulnerability", "ecosystems.csv"))
```

```{r}
exposure<- vroom(here("data_file/resources/vulnerability", "exposure.csv"))
```

```{r}
food<- vroom(here("data_file/resources/vulnerability", "food.csv"))
```

```{r}
habitat<- vroom(here("data_file/resources/vulnerability", "habitat.csv"))
```

```{r}
health<- vroom(here("data_file/resources/vulnerability", "health.csv"))
```

```{r}
infrastructure<- vroom(here("data_file/resources/vulnerability", "infrastructure.csv"))
```
```{r}
sensitivity<- vroom(here("data_file/resources/vulnerability", "sensitivity.csv"))
```

```{r}
vulnerability_delta<- vroom(here("data_file/resources/vulnerability", "vulnerability_delta.csv"))
```

```{r}
vulnerability<- vroom(here("data_file/resources/vulnerability", "vulnerability.csv"))
```

```{r}
water<- vroom(here("data_file/resources/vulnerability", "water.csv"))
```

### 1.3.9 CO2 emissions per capita

```{r}
CO2em<- vroom(here("raw_data", "yearly_full_release_long_format.csv"))
```
### 1.3.10 World Development Indicator

```{r}
WDI<- vroom(here("data_file", "wgidataset.xlsx"))
```


# 2. Data set up
cleaning joining merging
