---
title: "Valentine parts"
author: "Valentine Petzold"
format: html
---


# 1. Introduction
[Link to our github repository](https://github.com/clemence-code/Data_management_Project)

## 1.1 Description of the project - Research question

## 1.2 Description of the sources

OECD
World Bank 

+ links to the sources

## 1.3 Description of the data file

## 1.3.0 Set up
importation librairies

```{r}
library(vroom)
library(here)
library(ggplot2)
```
```{r}
here::i_am('Data_management_Project.Rproj')
HDI <- vroom(here("raw_data", "HDR25_Statistical_Annex_HDI_Table.xlsx."))
```
```{r}
Environmental_Policy_Stringency_Index<- vroom(here("raw_data", "OECD.ECO.MAD,DSD_EPS@DF_EPS,1.0,filtered,2025-11-19 13-27-34.xlsx"))
```
```{r}
Renewable_Electricity_Share<- vroom(here("raw_data", "yearly_full_release_long_format.csv"))
```
```{r}
Temperature_exposure<- vroom(here("raw_data", "OECD.ENV.EPI,DSD_ECH@EXT_TEMP_H,2.0,filtered,2025-11-19 13-23-57.xlsx"))
```

#### Unzipping the files
```{r}
zip_files <- list.files(
  here("raw_data"),
  pattern = "\\.zip$",
  full.names = TRUE
)

for (f in zip_files) {
  unzip(f, exdir = here("data_file"))
}
```


### 1.3.1 Historical exposure to extreme temperatures
- description rapide des variables
- number rows, columns, NA
- années
- pays
### 1.3.2 Human Development index

### 1.3.3 Income share of the top 10%

### 1.3.4 Environmental Policy Stringency

### 1.3.5 Share of electricity from renewable resources

### 1.3.6 Per capita energy use

### 1.3.7 Research and development as a share of GDP

### 1.3.8 ND-Gain vulnerability index

### 1.3.9 CO2 emissions per capita

# 2. Data set up
cleaning joining merging
